### 2020-01-29 article_draft.tex
More Changes

Work with \textcolor{red}{Simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However, these tests suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

@@

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Denote the estimator of $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.  Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. Letting $\rvv$ be distributed $\distv(\disto)$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a particular class of regions defined using $\ell_p$ norms. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align*}
	\Theta_0(r) = \left\{\omega : ||\omega||_2 \leq r\right\}.
\end{align*}
A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(||\rvv||_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
By constraining the possible regions we consider, we can now define our test in a simple algebraic form:
\begin{align*}
	\text{reject } H_0 \text{ if } ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2 \geq r_\alpha.
\end{align*}
Similarly, p-values can now be simply defined as $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$.
%The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.

% As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{||\boldsymbol{Z}_b||_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $||\sqrt{n}\hat{\boldsymbol{\psi}}||_p > c_{p, \alpha}$.

@@

% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.

% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
Above, we have used a norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This allows for creating tests and calculating p-values in a similar manner to the univariate case. 
% \textcolor{blue}{I don't understand the end of this sentence}.
However, this approach also works with more complicated functions.  For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$)
% \textcolor{blue}{(when $Z$ is sampled from what?)}
can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. The $\distv$ used to define $\Gamma_\distv$ will always be an estimated limiting distribution and the estimators considered for this method are all asymptotically linear. Thus, $\distv$ will always be a centered multivariate normal distribution so we can index our functions through $\vmat$, the variance covariance matrix of $\distv$, instead of $\distv$ itself. An example of $\Gamma_\vmat$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gamma_\vmat(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv. \label{gamma:pow}
\end{align}
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$

@@

To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

@@

\sh{\subsection{Summary of how simulations are run}}

\section{Simulation Study}
\label{sec:sim_stdy}
\subsection{Correlation}
\includegraphics[width = \linewidth]{uncor.jpg}
\includegraphics[width = \linewidth]{some_core.jpg}
\includegraphics[width = \linewidth]{lots_cor.jpg}
% A wide variety of simulation settings are considered in this section to show the breath of settings in which the adaptive test can be used.  The first setting considers independent draws from a random vector with mean zero and variance-covariance matrix $\Sigma$.  The measure of association between $Y$ and each covariate will be $\text{Cov}(Y, W_{j})/\text{Var}(W_j)$.  The dimension of the vector, denoted $d$ takes values $10, 50$, and $200$.  The number of correlated covariates will be zero, one, or $0.1, 0.2$, or $0.6$ of all the correlated covariates.  The correlation between each of the covariates will be either $0$ or $0.5$.  The sample sizes considered are $100$ and $500$.

@@

\begin{lemma}
	\label{lemma:cont_of_gam}
	The function:
	\begin{align*}
		\Gamma_{\Sigma}(t) = Pr_\distv(||\rvv^* + t|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \sim N(0, \Sigma)
	\end{align*}
	is continuous with respect to $\Sigma$ and $t$.  
\end{lemma}

@@

\begin{proof}
	The multivariate normal probability density function
\begin{align*}
	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)\right) 
\end{align*}	
is continuous with respect to both $\Sigma$ and $t$.

@@

It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): \textcolor{blue}{(dominating function shouldn't depend on $n$)}

\begin{align*}
	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{||x|| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{||x|| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
\end{align*}

@@

Because the normal cdf is continuous, we know the normal quantile function will be continuous as well. Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.  These findings imply the following:

>>>>

Work with \textcolor{red}{simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However, these tests suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

@@

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Let $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ be an estimator of $\boldsymbol{\psi}$, and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ in a model space $\mathcal{M}_0$.  Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. Letting $\rvv$ be distributed $\distv(\disto)$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a particular class of regions defined using $\ell_p$ norms. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align*}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}.
\end{align*}
A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
By constraining the possible regions we consider, we can now define our test by:
\begin{align*}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha.
\end{align*}
Similarly, p-values can now be defined as $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
%The quantity could also be used for a test, and since we know $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
% As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{\|\boldsymbol{Z}_b\|_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.

@@

% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Above, a norm mapped the distribution of $\rvv$ and value  of $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This distribution and value in $\mathbb{R}$ can be used to  calculate a p-value. 
% \textcolor{blue}{I don't understand the end of this sentence}. 
This method for finding $p$-values can be used with more complicated functions. We can think of the above test as a function of the test statistic, $\sqrt{n}\hat{\boldsymbol{\psi}}$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution.  For the purposes of a test, the distribution used to define any function will be the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ which is distributed according to a multivariate normal with a mean of zero. Because the variance covariance matrix of this multivariate normal (denoted $\Sigma$) \textcolor{blue}{is one-to-one with the possible distributions}, we will index our functions $\Gamma$ by $\Sigma$. 
% For every distribution $\distv$ with support contained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$. The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$) can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.  
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
An example of a more complicated function $\Gamma_\vmat$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider

\begin{align}
	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \overset{d}{=} \rvv. \label{gamma:pow}
\end{align}
% \textcolor{blue}{What is $\tilde\rvv \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$

@@

To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions.}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

@@

\section{Simulation Study}
\label{sec:sim_stdy}

\subsection{Correlation}

In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.  The Bonferroni based method computes a p-value for each covariate using a marginal linear regression.  If any p-value is smaller than the Bonferroni adjusted cutoff value, the null hypothesis is rejected. The method outlined by \citep{zhang_comment_2015} is similar to our method, but uses a parametric estimate of the correlation instead of using an influence function based estimator.  Four versions of our test are displayed in these plots. Our test that uses the $\ell_2$ norm, our test that uses the $\ell_\infty$ or max norm, and our test that selects over five possible $\ell_p$ norms.  The last version of our test selecs over many different versions of the following norm : $\|x\|_k = \sum_{i = 1}^k x_{(i)}^2$ where $x^2_{(i)}$ are the ordered statistics of $x^2$.

In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.

\begin{figure}[]
	\centering
\includegraphics[width = \linewidth]{uncor.jpg}
	\caption{Display of simulations for vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $0$ when $i \neq j$ and equal to 1 when $i = j$. Three different models for the outcome of interest ($Y$) will are considered. Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, in the first model $Y = \varepsilon$, in the second $Y = X_1 / 4$, and in the third $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$. Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$ are considered.}
	\label{fig:uncor}
\end{figure}

\begin{figure}[]
	\centering
\includegraphics[width = \linewidth]{some_core.jpg}
	\caption{The same simulation settings as those used in Figure \ref{fig:uncor}, but $\Sigma_{ij} = 0.5$ for $i \neq j$.}
	\label{fig:somecor}
\end{figure}

\begin{figure}[]
	\centering
\includegraphics[width = \linewidth]{lots_cor.jpg}
	\caption{The same simulation settings as those used in Figure \ref{fig:uncor}, but $\Sigma_{ij} = 0.8$ for $i \neq j$.}
	\label{fig:lotscor}
\end{figure}

We find that our procedure uses obtains relatively good power across a variety of settings.  While in certain settings our test is beaten by that of Zhang and Laber, this is to be expected because their procedure is tailor made for the setting in which there is normal data that follows a linear model. We also find that the adaptive version o the test consitently outperforms the Bonferroni based method in all settings except those in which there is no between-covariate correlation.

% A wide variety of simulation settings are considered in this section to show the breath of settings in which the adaptive test can be used.  The first setting considers independent draws from a random vector with mean zero and variance-covariance matrix $\Sigma$.  The measure of association between $Y$ and each covariate will be $\text{Cov}(Y, W_{j})/\text{Var}(W_j)$.  The dimension of the vector, denoted $d$ takes values $10, 50$, and $200$.  The number of correlated covariates will be zero, one, or $0.1, 0.2$, or $0.6$ of all the correlated covariates.  The correlation between each of the covariates will be either $0$ or $0.5$.  The sample sizes considered are $100$ and $500$.

@@

\begin{lemma}
	\label{lemma:cont_of_gam}
	The function:
	\begin{align*}
		\Gamma_{\Sigma}(t) = Pr_\distv(\|\tilde\rvv + t\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma)
	\end{align*}
	is continuous with respect to $\Sigma$ and $t$.  
\end{lemma}

@@

\begin{proof}
	The multivariate normal probability density function
\begin{align*}
	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)i\right) 
\end{align*}	
is continuous with respect to both $\Sigma$ and $t$.

@@

It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
This result and the dominated convergence theorem imply the corresponding CDF's are also continuous \textcolor{blue}{($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): (dominating function shouldn't depend on $n$)}  To find a dominating measure, assume that $\vmat_n^{-1}$ is close enough to $\vmat^{-1}$ so the smallest eigenvalue is within $\varepsilon$ then bound the pdf using this fact and that $(x - \mu)^\top \Sigma^{-1}(x - \mu) = (x - \mu)^\top ADA^{-1}(x - \mu) \leq \|(x - \mu)\|^2 c$ where $c$ is the largest eigen value (can be done to provide oposite direction as well).

\begin{align*}
	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{\|x\| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{\|x\| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
\end{align*}

@@

Because the normal cdf is continuous, we know the normal quantile function will be continuous as well. Potentially we can prove the existence of the inverse using the fact the CDF has a bounded derivative on all of $\mathbb{R}$.  Let $\Sigma_n \rightarrow \Sigma$ and $h_n \rightarrow h$.  Also, let $Q_n$ be a normal distribution with mean zero and variance-covaraince $\Sigma_n$.  These findings imply the following:

\begin{align*}
	\left|\Gamma_{\Sigma_n}(h) - \Gamma_{\Sigma}(h)\right| &= \left|Pr_{\distv_n}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)) - Pr_{\distv}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \Sigma_n) I\{\|t+h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{\|t+h\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
	&= \left|\int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} \phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
	&\leq \int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} |\phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
\end{align*}
The above quantity converges to zero by the dominated convergence theorem.

\begin{align*}
	& = \int_{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} |\phi(t, h, \Sigma_n)|dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, h, \Sigma)|dt \\
	& \leq \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} \phi(t, h, \Sigma_n)dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, h, \Sigma)dt \\
	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) + \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) - \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
	& \hspace{5em} \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) -  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
% Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
\end{align*}
% \textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
